\href{https://github.com/uds-datalab/PDBF}{PDBF} Documentation

### 2015-09-08 pdbf-doc.tex
now pdbf.jar should run independently of the current workingdir

@@

\newpage
\tableofcontents
\newpage

>>>>

\tableofcontents
\newpage

@@

\section{Getting started}
\begin{itemize}
\item Make sure you have a Java Runtime (version $>=$ 1.7) installed
\item \href{https://github.com/uds-datalab/PDBF/archive/gh-pages.zip}{Download the latest version}
\item Extract zip and change workingdir to extracted folder
\item Adjust config.cfg
\item Try to compile pdbf-doc.tex file with this command: java -jar pdbf.jar pdbf-doc.tex
\item Open pdbf-doc.html, this is the final output of the compilation process, if you rename it to ".pdf" it is also a valid pdf-document
\item Optionally you can attach the included vldb-Invaders.ova (Space invaders clone) or \href{https://github.com/uds-datalab/PDBF/releases/download/1.0.1/dsl.ova}{download the dsl.ova} (Damn small linux) VirtualBox image and attach it to the compiled PDBF file with this command: java -jar pdbf.jar --vm pdbf-doc.html vldb-Invaders.ova
\item You can play around with the minimal.tex file which contains a minimal example of PDBF usage
\item For further information take a look at the \href{http://uds-datalab.github.io/PDBF/}{documentation}
\end{itemize}
